Energy and the CES production function

### 2015-10-22 Articles/Article_EcolEcon_2015/EcolEcon_2015A.Rnw
Deleting CSP and Exp models from disk

<<Models_CSP>>=
fileNameCSP <- "EcolEcon2015ModelsCSP.rds"
if (!rerunModels){
  # load from the file on disk
  modelsCSP <- readRDS(fileNameCSP)
} else {
  #
  # Models that adhere to the cost-share theorem
  #

  modelsCSP <- list()
  # Output elasticities based on cost share principle
  alphaCSP <- 0.3 # Fraction of national accounts spent on capital
  betaCSP <- 0.7 # Fraction of national accounts spent on labor
  for (country in countries){
    for (adj in c("unadjusted", "adjusted")){
      # Replace with better code later. 
      # Would like to say cdModel(formula, data, factorShares=c(alpha_1 = 0.3, alpha_2 = 0.7, alpha_3 = 0))
      # or something like that.
      form <- keep_summands(formulas[[country]][[adj]], n=-3) # Remove energy
      yVar <- as.name(summands(form, n=1, right=FALSE))
      kVar <- as.name(summands(form, n=1))
      lVar <- as.name(summands(form, n=2))
      tVar <- as.name(summands(form, n=3))
      data <- historicalData[[country]]
      formula <- substitute(
        log(Y) - (alpha_1 * log(K) + alpha_2 * log(L)) ~ T,
        list( Y = yVar, K = kVar, L = lVar, T = tVar, A = alphaCSP, B = betaCSP)
      )
      # Cobb-Douglas
      cdModCSP <- 
        eval(substitute( 
          plm(formula, data = data, params = c(alpha_1 = 0.3, alpha_2 = 0.7, alpha_3 = 0.0), 
              optimize = FALSE),
          list(formula = formula)))

@@

      cesModCSP$coefficients <- 
        c(cesModCSP$coefficients, 
          c(delta_1 = as.vector(cesModCSP$coefficients["alpha_1"]),
            delta = 1,
            rho_1 = 0,
            rho = NA)
        )
      cesModCSP$handcrafted <- TRUE
      class(cesModCSP) <- setdiff(c("cesModel", class(cesModCSP)), "CDEmodel")
      # # Again, we need a customized "naturalCoeffs" attribute so that 
      # # the "naturalCoef" function will do the right thing.
      # # "naturalCoeffs" can be based on the same "naturalCoeffs"
      # # from the Cobb-Douglas model, but a few additions are needed.
      # attr(cesModCSP, "naturalCoeffs") <- 
      #   naturalCoef(cdModCSP) %>%
      #   mutate(
      #     delta_1 = naturalCoef(cdModCSP)[["alpha_1"]],
      #     delta = 1,
      #     rho_1 = 0, 
      #     rho = NA,
      #     sigma_1 = 1,
      #     sigma_12 = 1,
      #     sigma = NA,
      #     sigma_12_3 = NA
      #   )
      # # Add output elasticities (as a function of time) to this model.
      # # This would have been done by a "fortify" function, 
      # # but this is not a typical CES model, so we can't "fortify" it.
      # # Add other metadata, too.
      # cesModCSP$data <- cesModCSP$data %>%
      #   mutate(
      #     oe1 = alphaCSP,
      #     oe2 = betaCSP,
      #     oe3 = 0,
      #     Country = country, 
      #     flavor  = ifelse(adj=="unadjusted", "Unadjusted", "Quality-adjusted"),
      #     energy  = "Without energy",
      #     model   = "CES", 
      #     nest    = "kl",
      #     CSP     = "w/ CSP"
      #   )
      modelsCSP[[country]][[adj]][["noE"]][["CES"]][["kl"]] <- cesModCSP
    }
  }
  # Save cost-share theorem models to disk.
  saveRDS(modelsCSP, file=fileNameCSP)
}

@@

<<Models_Exp>>=
fileNameExp <- "EcolEcon2015ModelsExp.rds"
if (!rerunModels){
  # load from the file on disk
  modelsExp <- readRDS(fileNameExp)
} else {
  #
  # Models that are exponential only, y = A * exp(lambda*t)
  #
  modelsExp <- list()
  alphaExp <- 0
  betaExp <- 0
  gammaExp <- 0
  for (country in countries){
    # Replace with better code later. 
    # Would like to say cdModel(formula, data, factorShares=c(alpha_1 = 0, alpha_2 = 0, alpha_3 = 0))
    # or something like that.
    form <- keep_summands(formulas[[country]][["unadjusted"]], n = c(-1, -2, -3)) # Keep none of the factors of production
    yVar <- as.name(summands(form, n=1, right=FALSE))
    tVar <- as.name(summands(form, n=1))
    data <- historicalData[[country]]
    expMod <- lm(log(eval(yVar)) ~ eval(tVar), data=data)
    attr(expMod, "naturalCoeffs") <- data.frame(lambda=coef(expMod)[[2]],
                                                  logscale=coef(expMod)[[1]], 
                                                  scale=exp(coef(expMod)[[1]]),
                                                  alpha_1=alphaExp,
                                                  alpha_2=betaExp, 
                                                  alpha_3=gammaExp)
    expMod$formula <- form
    sdata <- subset(data, select=all.vars(form))
    sdata <- data[complete.cases(sdata), unique(c(all.vars(form), names(data)))]
    expMod$data <- sdata
    expMod$response <- sdata$iGDP 
    modelsExp[[country]] <- expMod
  }
  # Save exponential models to disk.
  saveRDS(modelsExp, file=fileNameExp)
}

>>>>

<<Models_CSP>>=
#
# Models that adhere to the cost-share principle
# 
modelsCSP <- list()
# Output elasticities based on cost share principle
alphaCSP <- 0.3 # Fraction of national accounts spent on capital
betaCSP <- 0.7 # Fraction of national accounts spent on labor
for (country in countries){
  for (adj in c("unadjusted", "adjusted")){
    # Replace with better code later. 
    # Would like to say cdModel(formula, data, factorShares=c(alpha_1 = 0.3, alpha_2 = 0.7, alpha_3 = 0))
    # or something like that.
    form <- keep_summands(formulas[[country]][[adj]], n=-3) # Remove energy
    yVar <- as.name(summands(form, n=1, right=FALSE))
    kVar <- as.name(summands(form, n=1))
    lVar <- as.name(summands(form, n=2))
    tVar <- as.name(summands(form, n=3))
    data <- historicalData[[country]]
    formula <- substitute(
      log(Y) - (alpha_1 * log(K) + alpha_2 * log(L)) ~ T,
      list( Y = yVar, K = kVar, L = lVar, T = tVar, A = alphaCSP, B = betaCSP)
    )
    # Cobb-Douglas
    cdModCSP <- 
      eval(substitute( 
        plm(formula, data = data, params = c(alpha_1 = 0.3, alpha_2 = 0.7, alpha_3 = 0.0), 
            optimize = FALSE),
        list(formula = formula)))

@@

    cesModCSP$coefficients <- 
      c(cesModCSP$coefficients, 
        c(delta_1 = as.vector(cesModCSP$coefficients["alpha_1"]),
          delta = 1,
          rho_1 = 0,
          rho = NA)
      )
    cesModCSP$handcrafted <- TRUE
    class(cesModCSP) <- setdiff(c("cesModel", class(cesModCSP)), "CDEmodel")
    # # Again, we need a customized "naturalCoeffs" attribute so that 
    # # the "naturalCoef" function will do the right thing.
    # # "naturalCoeffs" can be based on the same "naturalCoeffs"
    # # from the Cobb-Douglas model, but a few additions are needed.
    # attr(cesModCSP, "naturalCoeffs") <- 
    #   naturalCoef(cdModCSP) %>%
    #   mutate(
    #     delta_1 = naturalCoef(cdModCSP)[["alpha_1"]],
    #     delta = 1,
    #     rho_1 = 0, 
    #     rho = NA,
    #     sigma_1 = 1,
    #     sigma_12 = 1,
    #     sigma = NA,
    #     sigma_12_3 = NA
    #   )
    # # Add output elasticities (as a function of time) to this model.
    # # This would have been done by a "fortify" function, 
    # # but this is not a typical CES model, so we can't "fortify" it.
    # # Add other metadata, too.
    # cesModCSP$data <- cesModCSP$data %>%
    #   mutate(
    #     oe1 = alphaCSP,
    #     oe2 = betaCSP,
    #     oe3 = 0,
    #     Country = country, 
    #     flavor  = ifelse(adj=="unadjusted", "Unadjusted", "Quality-adjusted"),
    #     energy  = "Without energy",
    #     model   = "CES", 
    #     nest    = "kl",
    #     CSP     = "w/ CSP"
    #   )
    modelsCSP[[country]][[adj]][["noE"]][["CES"]][["kl"]] <- cesModCSP
  }
}

@@

<<Models_Exp>>=
#
# Models that are exponential only, y = A * exp(lambda*t)
#
modelsExp <- list()
alphaExp <- 0
betaExp <- 0
gammaExp <- 0
for (country in countries){
  # Replace with better code later. 
  # Would like to say cdModel(formula, data, factorShares=c(alpha_1 = 0, alpha_2 = 0, alpha_3 = 0))
  # or something like that.
  form <- keep_summands(formulas[[country]][["unadjusted"]], n = c(-1, -2, -3)) # Keep none of the factors of production
  yVar <- as.name(summands(form, n=1, right=FALSE))
  tVar <- as.name(summands(form, n=1))
  data <- historicalData[[country]]
  expMod <- lm(log(eval(yVar)) ~ eval(tVar), data=data)
  attr(expMod, "naturalCoeffs") <- data.frame(lambda=coef(expMod)[[2]],
                                              logscale=coef(expMod)[[1]], 
                                              scale=exp(coef(expMod)[[1]]),
                                              alpha_1=alphaExp,
                                              alpha_2=betaExp, 
                                              alpha_3=gammaExp)
  expMod$formula <- form
  sdata <- subset(data, select=all.vars(form))
  sdata <- data[complete.cases(sdata), unique(c(all.vars(form), names(data)))]
  expMod$data <- sdata
  expMod$response <- sdata$iGDP 
  modelsExp[[country]] <- expMod
}
